### 2015-07-06 paper.tex
project creation

\documentclass{chi-ext}
% Please be sure that you have the dependencies (i.e., additional LaTeX packages) to compile this example.
% See http://personales.upv.es/luileito/chiext/

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
% \copyrightinfo{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
% {\emph{IHM14}}, 28-31 Octobre, 2014, Lille, France. \\
% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
% DOI string from ACM form confirmation}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

\title{IHM \LaTeX\ Ext. Abstracts Template}

\numberofauthors{6}
% Notice how author names are alternately typesetted to appear ordered in 2-column format;
% i.e., the first 4 autors on the first column and the other 4 auhors on the second column.
% Actually, it's up to you to strictly adhere to this author notation.
\author{
  \alignauthor{
  	\textbf{Premier Auteur}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author1@anotherco.com}
  }\alignauthor{
  	\textbf{Quatrième Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author5@anotherco.com}
  }
  \vfil
  \alignauthor{
  	\textbf{Deuxième Auteur}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author2@anotherco.com}
  }\alignauthor{
  	\textbf{Cinquième Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author6@anotherco.com}
  }
  \vfil
  \alignauthor{
  	\textbf{Troisième Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author3@anotherco.com}
  }\alignauthor{
  	\textbf{Sixième Author}\\
  	\affaddr{AuthorCo, Inc.}\\
  	\affaddr{123 Author Ave.}\\
  	\affaddr{Authortown, PA 54321 USA}\\
  	\email{author7@anotherco.com}
  }
}

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{CHI LaTeX Extended Abstracts Template}
\def\plainauthor{Luis A. Leiva}
\def\plainkeywords{Guides, instructions, author's kit, conference publications}
\def\plaingeneralterms{Documentation, Standardization}

\hypersetup{
  % Your metadata go here
  pdftitle={\plaintitle},
  pdfauthor={\plainauthor},  
  pdfkeywords={\plainkeywords},
  pdfsubject={\plaingeneralterms},
  % Quick access to color overriding:
  %citecolor=black,
  %linkcolor=black,
  %menucolor=black,
  %urlcolor=black,
}

\usepackage{graphicx}   % for EPS use the graphics package instead
\usepackage{balance}    % useful for balancing the last columns
\usepackage{bibspacing} % save vertical space in references
%\usepackage{hyperref}
%\hypersetup{colorlinks=false}

%\widowpenalty=10000
%\clubpenalty=10000

\begin{document}

\maketitle

\begin{abstract}
Dans cet exemple nous décrivons les règles de formatage pour les Travaux en Cours (TeC) IHM, ainsi que des conseils de rédaction.
%Ne changez pas la taille des pages ou les paramètres des pages.
Veuillez lire ce document, même si vous avez déjà soumis : il peut y avoir des différences.
\end{abstract}

\keywords{\plainkeywords}
\textcolor{red}{Champs requis dans la version finale}

\category{H.5.m}{Information interfaces and presentation (e.g., HCI)}{Miscellaneous}. 
%See \cite{ACMCCS} 
Voir : \url{http://www.acm.org/about/class/1998/} 
pour une description du ACM Classification system.
\textcolor{red}{Champs requis dans la version finale}

\terms{\plaingeneralterms}
\textcolor{red}{Champs requis dans la version finale}

% =============================================================================
\section{Introduction}
% =============================================================================
Ce format est à utiliser pour les TeC, qui sont publiés dans les actes étendus. 
Ces articles doivent conserver une apparence consistante et de qualité. 
Nous vous demandons donc de suivre ces règles de formatage simples.
Dans l'idée, vous devez formatter votre papier de la même façon que ce document.
La façon la plus simple est de télécharger le template sur le site web de la conférence et de remplacer le contenu par votre propre matériel.

% =============================================================================
\section{Copyright}
% =============================================================================

Les auteurs conservent le copyright pour les articles publiés en TeC.
Ces articles ne sont pas considérés comme des publications d'archive, mais sont tout de même publiés sur la Digital Library ACM.
Le fait que vous conserviez le copyright signifie que vous êtes libre de réutiliser votre matériel comme vous l'entendez, y compris soumettre un article à propos de ce matériel à une autre conférence ou journal.
Les auteurs donnent à l'ACM une permission sans réseve de publier les soumissions acceptées dans les actes étendus d'IHM sans considération ou rémunération supplémentaire.

% =============================================================================
\section{Formatage du texte}
% =============================================================================
Veuillez utiliser une police Verdana de 8.5 points, ou toute autre police sans sérif ayant une apparence proche de Verdana, utilisée dans ce document.
La police Arial en 9 points est un substitut raisonnable car elle a une taille similaire.
Veuillez n'utiliser une police à sérif ou de taille différente que pour des cas spéciaux, tels que mettre en avant du code source.
De plus voici un exemple de note de bas de page.\footnote{Utilisez les notes de bas de page avec parcimonie, et que si nécessaire.}
Comme précisé dans la note de bas de page, les notes de bas de page doivent être rarement utilisées.

\subsection{Langue, style, et contenu}
% -----------------------------------------------------------------------------
La langue officielle d'IHM est le français. Les soumissions en anglais sont autorisées, cependant en français comme en anglais la qualité de rédaction est un critère d'évaluation. Nous rappelons que la \href{http://www.sigchi.org/conferences/organizing-a-sigchi-sponsored-conference}{politique de l'ACM} autorise la publication d'une traduction en anglais d'un article écrit dans une langue différente.
Les règles de typographie doivent être adaptées à la langue de l'article.
Pour vous assurer d'être compréhensible, veuillez suivre ces conseils :

\begin{itemize}\compresslist
\item 	
Utilisez un style direct.
Utilisez des structures de phrase simples.
Essayez d'éviter des phrases longues avec des structures compliquées.
Utilisez les point-virgule avec précaution.
\item 	
Utilisez un vocabulaire courant et usuel (ex. : utilisez le mot « inhabituel » plutôt que « ésotérique »).
\item 	
Définissez ou expliquez brièvement chaque terme technique.
La terminologie courante dans votre discipline peut être différente de celle dans d'autres disciplines.
\item 	
Détaillez tous les acronymes la première fois que vous les utilisez dans votre texte.
Par exemple « Interaction Homme-Machine (IHM) »
\item 	
Expliquez les références locales (ex. : tout le monde ne connait pas tous les noms de ville dans une région particulière).
\item 	
Expliquez les commentaires d'initiés.
Assurez vous que tout le monde comprend toutes les références à ce que vous ne décrivez pas (ex. : ne supposez pas que tout le monde a déjà utilisé un Mac ou une application particulière).
\item 	
Expliquez le langage familier ou les jeux de mots.
Comprendre une expression telle que « poisson d'avril » nécessite des connaissance culturelles françaises.
L'humour et l'ironie sont difficiles à traduire.
\item 	
Utilisez des formes non ambigües selon la culture, tel que les dates, heures, monnaies et nombres (ex. : « 1-5-14 » ou « 5/1/14 » qui peuvent vouloir dire 5 janvier ou 1er mai, ou « sept heures » peut vouloir dire 7h ou 19h.).
\item 	
Faites attention avec l'utilisation de pronoms spécifiques au genre (il, elle) et autres mots dépendants du genre (ex. : homme-mois).
Utilisez un langage inclusif (ex. : il ou elle, ils ou elles, personne-mois) qui sont indépendants du genre.
Si nécessaire, vous pouvez utiliser « il » et « elle » en alternant dans vos phrases, de manière à équilibrer les genres. 
\end{itemize}

% =============================================================================
\section{Figures}
% =============================================================================

\marginpar{
\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/lille.eps}
  \caption{Une figure dans la marge.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}
}

Les exemples dans cette page et les suivantes devraient vous donner une idée de comment les photos et screenshots doivent être placés dans le template. 
Assurez-vous que vos images soient assez grandes pour que les détails soient visibles et clairs.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/lille.eps}
  \caption{Ajoutez une légende en dessous de chaque image.}
  \label{fig:sample}
\end{figure}

Votre document peut utiliser des figures en couleurs, qui sont comprises dans les limites de pages ; les figures doivent rester lisibles si le document est imprimé en noir et blanc.
Vous pouvez utiliser la commande \LaTeX \texttt{marginpar} pour insérer des figures dans la marge de gauche (voir \autoref{fig:marginparsample}).

% =============================================================================
\section{Références et Citations}
% =============================================================================
Utilisez une liste numérotée à la fin de l'article, par ordre alphabétique du premier auteur, et référencée par des numéros entre crochets~\cite{mbl-ihm-97,coutaz-ihm-97,guiard-jmb-87}
Pour les articles dans des actes de conférences, indiquez le titre du papier et une version abrégée du nom de la conférence (ex. : pour les actes d'IHM 2001, utilisez « Actes d'IHM 2001 »).
N'ajoutez pas le lieu de la conférence ou la date exacte ; ajoutez les numéros de pages si disponibles.
Voyez des exemples de citations à la fin de ce document.

Vos références doivent être du matériel publié et accessible au public.
Les rapports internes peuvent être cités si ils sont aisément accessibles (ex. : vous donnez l'adresse pour obtenir le rapport dans votre citation) et peuvent être obtenus par n'importe quel lecteur pour une somme modique.
Les informations propriétaires ne devraient pas être citées.
Les communications privées doivent être mentionnées dans le texte principal, pas référencées (ex. : [Georges Abitbol, personal communication]).

% =============================================================================
\section{Produire et tester le fichier PDF}
% =============================================================================
Nous vous recommandons de produire une version PDF de votre soumission bien avant la date butoir.
En plus de vérifier que vous pouvez produire un PDF, vous devrez vérifier que (a) la longueur du fichier reste dans les limites fixéers par la catégorie visée, (b) le fichier PDF n'excède pas 4 Mo, et (c) le fichier peut être lu et imprimé avec Adobe Acrobat Reader.
Testez votre PDF en le visionnant et l'imprimant avec le même logiciel que nous quand nous le recevrons, Adobe Acrobat Reader 10.
Ce logiciel est très répandu et gratuit~\cite{Acrobat10}.

% =============================================================================
\section{Dummy text}
% =============================================================================
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ut eros semper lectus vehicula elementum. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam quis mi sapien. Suspendisse potenti. Mauris ultrices euismod velit sed dictum. Nullam auctor, nulla tincidunt dapibus suscipit, velit leo convallis metus, vel commodo libero erat in dolor. In laoreet porttitor ligula, porta blandit lectus consequat quis.

Nam ut eros dui. Mauris volutpat elit metus, euismod pellentesque purus. In hac habitasse platea dictumst. Nullam consectetur lacinia interdum. Sed nec blandit nisi. Proin in nulla purus, sit amet iaculis tortor. Ut dapibus pellentesque nulla in interdum. Nunc at velit felis. Curabitur euismod neque eu orci varius in pharetra sem interdum. Morbi in mauris ac risus iaculis dapibus id in magna. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.

Aliquam consectetur quam sed odio varius vitae rhoncus urna fermentum. Phasellus viverra diam non justo porttitor varius. Integer ultrices accumsan lectus eget mollis. Nulla et leo sit amet nunc ornare rutrum sit amet ac dui. Cras vehicula accumsan purus nec fermentum. Mauris viverra condimentum metus, ut posuere quam laoreet nec. Phasellus massa tellus, ullamcorper nec porta sed, aliquet vitae nulla. Phasellus non tortor mauris. Cras ullamcorper egestas erat, vel rutrum elit viverra a. Donec in nisl ut est facilisis blandit. Quisque congue accumsan risus, ut venenatis magna vulputate vel. Nam commodo sapien vel mauris adipiscing nec dictum quam congue. Phasellus tempor vestibulum nisl quis blandit. Nullam condimentum auctor nibh, quis elementum libero tristique.

\section{Remerciements}
Nous remercions toutes les personnes qui ont successivement modifié ce format. Nous nous sommes basés sur la version distribuée pour CHI 2013, et qui est à ce jour la version officielle \url{http://personales.upv.es/luileito/chiext/}.

\section{Format des références}
Les références doivent utiliser la même taille de police que le reste du texte.
% REFERENCES FORMAT
% References must be the same font size as other body text.

\balance
\bibliographystyle{acm-sigchi}
\bibliography{ref}

\end{document}

### 2015-07-07 paper.tex
Paper general structure

@@
 
-\title{IHM \LaTeX\ Ext. Abstracts Template}
+\title{Test of Adaptable User Interfaces}
 
-\numberofauthors{6}
+\numberofauthors{4}
 % Notice how author names are alternately typesetted to appear ordered in 2-column format;
@@
   \alignauthor{
-  	\textbf{Premier Auteur}\\
+  	\textbf{Nelson}\\
   	\affaddr{AuthorCo, Inc.}\\
@@
   }\alignauthor{
-  	\textbf{Quatrième Author}\\
+  	\textbf{Julien}\\
   	\affaddr{AuthorCo, Inc.}\\
@@
   \alignauthor{
-  	\textbf{Deuxième Auteur}\\
+  	\textbf{Lydie}\\
   	\affaddr{AuthorCo, Inc.}\\
@@
   }\alignauthor{
-  	\textbf{Cinquième Author}\\
+  	\textbf{Sophie}\\
   	\affaddr{AuthorCo, Inc.}\\
@@
   }
-  \vfil
-  \alignauthor{
-  	\textbf{Troisième Author}\\
-  	\affaddr{AuthorCo, Inc.}\\
-  	\affaddr{123 Author Ave.}\\
-  	\affaddr{Authortown, PA 54321 USA}\\
-  	\email{author3@anotherco.com}
-  }\alignauthor{
-  	\textbf{Sixième Author}\\
-  	\affaddr{AuthorCo, Inc.}\\
-  	\affaddr{123 Author Ave.}\\
-  	\affaddr{Authortown, PA 54321 USA}\\
-  	\email{author7@anotherco.com}
-  }
 }
@@
 % Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
-\def\plaintitle{CHI LaTeX Extended Abstracts Template}
-\def\plainauthor{Luis A. Leiva}
+\def\plaintitle{Test of Adaptable User Interfaces}
+\def\plainauthor{Nelson Mariano Leite Neto}
 \def\plainkeywords{Guides, instructions, author's kit, conference publications}
@@
 \begin{abstract}
-Dans cet exemple nous décrivons les règles de formatage pour les Travaux en Cours (TeC) IHM, ainsi que des conseils de rédaction.
-%Ne changez pas la taille des pages ou les paramètres des pages.
-Veuillez lire ce document, même si vous avez déjà soumis : il peut y avoir des différences.
+TODO - Lorem ipsum sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo.
+Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt.
+Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem.
 \end{abstract}
@@
 % =============================================================================
-Ce format est à utiliser pour les TeC, qui sont publiés dans les actes étendus. 
-Ces articles doivent conserver une apparence consistante et de qualité. 
-Nous vous demandons donc de suivre ces règles de formatage simples.
-Dans l'idée, vous devez formatter votre papier de la même façon que ce document.
-La façon la plus simple est de télécharger le template sur le site web de la conférence et de remplacer le contenu par votre propre matériel.
+TODO
 
 % =============================================================================
-\section{Copyright}
+\section{Related Work}
 % =============================================================================
-
-Les auteurs conservent le copyright pour les articles publiés en TeC.
-Ces articles ne sont pas considérés comme des publications d'archive, mais sont tout de même publiés sur la Digital Library ACM.
-Le fait que vous conserviez le copyright signifie que vous êtes libre de réutiliser votre matériel comme vous l'entendez, y compris soumettre un article à propos de ce matériel à une autre conférence ou journal.
-Les auteurs donnent à l'ACM une permission sans réseve de publier les soumissions acceptées dans les actes étendus d'IHM sans considération ou rémunération supplémentaire.
+TODO
 
 % =============================================================================
-\section{Formatage du texte}
+\section{Case Study}
 % =============================================================================
-Veuillez utiliser une police Verdana de 8.5 points, ou toute autre police sans sérif ayant une apparence proche de Verdana, utilisée dans ce document.
-La police Arial en 9 points est un substitut raisonnable car elle a une taille similaire.
-Veuillez n'utiliser une police à sérif ou de taille différente que pour des cas spéciaux, tels que mettre en avant du code source.
-De plus voici un exemple de note de bas de page.\footnote{Utilisez les notes de bas de page avec parcimonie, et que si nécessaire.}
-Comme précisé dans la note de bas de page, les notes de bas de page doivent être rarement utilisées.
-
-\subsection{Langue, style, et contenu}
-% -----------------------------------------------------------------------------
-La langue officielle d'IHM est le français.
-Les soumissions en anglais sont autorisées, cependant en français comme en anglais la qualité de rédaction est un critère d'évaluation.
-Nous rappelons que la \href{http://www.sigchi.org/conferences/organizing-a-sigchi-sponsored-conference}{politique de l'ACM} autorise la publication d'une traduction en anglais d'un article écrit dans une langue différente.
-Les règles de typographie doivent être adaptées à la langue de l'article.
-Pour vous assurer d'être compréhensible, veuillez suivre ces conseils :
-
-\begin{itemize}\compresslist
-\item 	
-Utilisez un style direct.
-Utilisez des structures de phrase simples.
-Essayez d'éviter des phrases longues avec des structures compliquées.
-Utilisez les point-virgule avec précaution.
-\item 	
-Utilisez un vocabulaire courant et usuel (ex. : utilisez le mot « inhabituel » plutôt que « ésotérique »).
-\item 	
-Définissez ou expliquez brièvement chaque terme technique.
-La terminologie courante dans votre discipline peut être différente de celle dans d'autres disciplines.
-\item 	
-Détaillez tous les acronymes la première fois que vous les utilisez dans votre texte.
-Par exemple « Interaction Homme-Machine (IHM) »
-\item 	
-Expliquez les références locales (ex. : tout le monde ne connait pas tous les noms de ville dans une région particulière).
-\item 	
-Expliquez les commentaires d'initiés.
-Assurez vous que tout le monde comprend toutes les références à ce que vous ne décrivez pas (ex. : ne supposez pas que tout le monde a déjà utilisé un Mac ou une application particulière).
-\item 	
-Expliquez le langage familier ou les jeux de mots.
-Comprendre une expression telle que « poisson d'avril » nécessite des connaissance culturelles françaises.
-L'humour et l'ironie sont difficiles à traduire.
-\item 	
-Utilisez des formes non ambigües selon la culture, tel que les dates, heures, monnaies et nombres (ex.
-: « 1-5-14 » ou « 5/1/14 » qui peuvent vouloir dire 5 janvier ou 1er mai, ou « sept heures » peut vouloir dire 7h ou 19h.).
-\item 	
-Faites attention avec l'utilisation de pronoms spécifiques au genre (il, elle) et autres mots dépendants du genre (ex. : homme-mois).
-Utilisez un langage inclusif (ex. : il ou elle, ils ou elles, personne-mois) qui sont indépendants du genre.
-Si nécessaire, vous pouvez utiliser « il » et « elle » en alternant dans vos phrases, de manière à équilibrer les genres. 
-\end{itemize}
+TODO
 
 % =============================================================================
-\section{Figures}
-% =============================================================================
+\section{Approach: generating test scripts for UI testing from abstract descriptions}
+% =========================================
+\subsection{Principle}
+TODO
 
-\marginpar{
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=\marginparwidth]{images/lille.eps}
-  \caption{Une figure dans la marge.}
-  \label{fig:marginparsample}
-  \end{center}  
-\end{figure}
-}
+\subsection{Principles put into Practice}
+TODO
 
-Les exemples dans cette page et les suivantes devraient vous donner une idée de comment les photos et screenshots doivent être placés dans le template. 
-Assurez-vous que vos images soient assez grandes pour que les détails soient visibles et clairs.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{images/lille.eps}
-  \caption{Ajoutez une légende en dessous de chaque image.}
-  \label{fig:sample}
-\end{figure}
-
-Votre document peut utiliser des figures en couleurs, qui sont comprises dans les limites de pages ; les figures doivent rester lisibles si le document est imprimé en noir et blanc.
-Vous pouvez utiliser la commande \LaTeX \texttt{marginpar} pour insérer des figures dans la marge de gauche (voir \autoref{fig:marginparsample}).
+\subsection{Discussion and Analysis}
+TODO
 
 % =============================================================================
-\section{Références et Citations}
+\section{Conclusions and Perspectives}
 % =============================================================================
-Utilisez une liste numérotée à la fin de l'article, par ordre alphabétique du premier auteur, et référencée par des numéros entre crochets~\cite{mbl-ihm-97,coutaz-ihm-97,guiard-jmb-87}
-Pour les articles dans des actes de conférences, indiquez le titre du papier et une version abrégée du nom de la conférence (ex. : pour les actes d'IHM 2001, utilisez « Actes d'IHM 2001 »).
-N'ajoutez pas le lieu de la conférence ou la date exacte ; ajoutez les numéros de pages si disponibles.
-Voyez des exemples de citations à la fin de ce document.
-
-Vos références doivent être du matériel publié et accessible au public.
-Les rapports internes peuvent être cités si ils sont aisément accessibles (ex.
-: vous donnez l'adresse pour obtenir le rapport dans votre citation) et peuvent être obtenus par n'importe quel lecteur pour une somme modique.
-Les informations propriétaires ne devraient pas être citées.
-Les communications privées doivent être mentionnées dans le texte principal, pas référencées (ex. : [Georges Abitbol, personal communication]).
-
-% =============================================================================
-\section{Produire et tester le fichier PDF}
-% =============================================================================
-Nous vous recommandons de produire une version PDF de votre soumission bien avant la date butoir.
-En plus de vérifier que vous pouvez produire un PDF, vous devrez vérifier que (a) la longueur du fichier reste dans les limites fixéers par la catégorie visée, (b) le fichier PDF n'excède pas 4 Mo, et (c) le fichier peut être lu et imprimé avec Adobe Acrobat Reader.
-Testez votre PDF en le visionnant et l'imprimant avec le même logiciel que nous quand nous le recevrons, Adobe Acrobat Reader 10.
-Ce logiciel est très répandu et gratuit~\cite{Acrobat10}.
-
-% =============================================================================
-\section{Dummy text}
-% =============================================================================
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Duis ut eros semper lectus vehicula elementum.
-Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam quis mi sapien.
-Suspendisse potenti.
-Mauris ultrices euismod velit sed dictum.
-Nullam auctor, nulla tincidunt dapibus suscipit, velit leo convallis metus, vel commodo libero erat in dolor.
-In laoreet porttitor ligula, porta blandit lectus consequat quis.
-
-Nam ut eros dui.
-Mauris volutpat elit metus, euismod pellentesque purus.
-In hac habitasse platea dictumst.
-Nullam consectetur lacinia interdum.
-Sed nec blandit nisi.
-Proin in nulla purus, sit amet iaculis tortor.
-Ut dapibus pellentesque nulla in interdum.
-Nunc at velit felis.
-Curabitur euismod neque eu orci varius in pharetra sem interdum.
-Morbi in mauris ac risus iaculis dapibus id in magna.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
-
-Aliquam consectetur quam sed odio varius vitae rhoncus urna fermentum.
-Phasellus viverra diam non justo porttitor varius.
-Integer ultrices accumsan lectus eget mollis.
-Nulla et leo sit amet nunc ornare rutrum sit amet ac dui.
-Cras vehicula accumsan purus nec fermentum.
-Mauris viverra condimentum metus, ut posuere quam laoreet nec.
-Phasellus massa tellus, ullamcorper nec porta sed, aliquet vitae nulla.
-Phasellus non tortor mauris.
-Cras ullamcorper egestas erat, vel rutrum elit viverra a.
-Donec in nisl ut est facilisis blandit.
-Quisque congue accumsan risus, ut venenatis magna vulputate vel.
-Nam commodo sapien vel mauris adipiscing nec dictum quam congue.
-Phasellus tempor vestibulum nisl quis blandit.
-Nullam condimentum auctor nibh, quis elementum libero tristique.
-
-\section{Remerciements}
-Nous remercions toutes les personnes qui ont successivement modifié ce format.
-Nous nous sommes basés sur la version distribuée pour CHI 2013, et qui est à ce jour la version officielle \url{http://personales.upv.es/luileito/chiext/}.
-
-\section{Format des références}
-Les références doivent utiliser la même taille de police que le reste du texte.
-% REFERENCES FORMAT
-% References must be the same font size as other body text.
+TODO
 

### 2015-07-07 paper.tex
Add ideas for related Work part

@@
 % =============================================================================
-TODO
+Automation of adaptive UI testing may be achieved by several means :
+- using Finite State Machine-based modeling which suffers scaling problems [TODO: ref]
+- creating an abstraction of the UI which is then tested in place of the UI itself [TODO: ref Sophie's paper]
+- automated planning for hierarchical test case generation may be used which involves genetic algorithms [TODO: ref]
+- using "capture and replay" method is rejected, as it would involve one capture per version [TODO: ref]
 

### 2015-07-07 paper.tex
Add testing context to Related Work

--- 2015-07-07 paper.tex
@@
 % =============================================================================
-TODO
+Quality is very important in the software industry, and so are tests. They have been extensively studied by literature [TODO: some refs].
+In a more modern context, Continuous Integration (CI) has been gaining popularity, hence is the need of automated tests.
+An automated test is usually generated for the exact goal to achieve, then is executed and its results are compared to those expected, finally a report is constructed with a summary of the failures encountered.
+The report can be easily generated by IDE plugins as long as tests are well designed and use testing libraries (like JUnit).
+The increasing popularity of web-based softwares has obliged to develop tools to perform tests on these devices.
+Among them, are Selenium for browser-based applications, and Selendroid for Android applications.
+Furthermore, GUIs have proven to be difficult to test, requiring new ways to verify them.
+So automation of UI testing may be achieved by several means :
+- using Finite State Machine-based modeling which suffers scaling problems [TODO: ref]
+- creating an abstraction of the UI which is then tested in place of the UI itself [TODO: ref Sophie's paper]
+- automated planning for hierarchical test case generation may be used which involves genetic algorithms [TODO: ref]
+- using "capture and replay" method is rejected, as it would involve one capture per version [TODO: ref]
 

### 2015-07-07 paper.tex
First vertion of the introduction section

--- 2015-07-07 paper.tex
@@
 % =============================================================================
-TODO
+Nowadays, with the rise of mobile devices such as notebooks, smartphones, smartwatches and tablets, we have computer systems running everywhere and in different \textit{contexts of use}, which involves three factors: the \textit{platform}, \textit{environment} and \textit{the user}~\cite{ui-eric-plasticity-vs-responsive}.
+These factors affect the interaction between the user and the system.
+This interaction happens through the \textit{user interface} (UI) and users have to deal with different UIs adapted to several contexts.
+Hence the term \textit{adaptable user interfaces}.
+All this allows us to see that today developing UIs can be as complex as developing the core of the system.
+There are several questions to be considered, among them: quality.
+\textit{Software Testing} is one of the most used ways in the industry to assure quality~\cite{test-hdr-lydie}.
+It can be defined as a process, or a series of processes, designed to ensure computer code does what it was designed to do and, conversely, that it does not anything unintended~\cite{test-art-of-testing}.
+What is the impact of adaptable user interfaces in software testing?
+Are there tools ready to test these adaptable UIs?
+
+Answering these questions motivates the development of this project.
+In this work, we focus on the scenario of having different UIs for the same system.
+These UIs can be adapted to different devices or have different versions for the same device.
+For instance, we used as case study, a smart home energy management system prototype with four equivalent versions: three for web and one for mobile environment.
+This exposes the problem in which we focus: the repetitive work of writing test scripts for different versions of the UIs of the same system.
+
+Our contribution is the approach of automatically generate test scripts for each version of the UI of the same system from scripts written in a higher-level language.
+In other words, testers would be able to write test cases for all the versions using abstract descriptions.
+A tool would be responsible for interpreting these descriptions and generating test scripts ready to be executed for each version of the UI.
+
+This paper is structured as follows.
+First, the related work is presented, explaining several concepts about test automation, UI testing and tools.
+Then, we explain the case study used in this research.
+Next, we show how test scripts can be generated from abstract descriptions using an existing tool.
+Finally, the conclusions that summarize our current results and proposed perspectives.
 

### 2015-07-07 paper.tex
Adding some corrections to Introduction

@@
 % =============================================================================
-Nowadays, with the rise of mobile devices such as notebooks, smartphones, smartwatches and tablets, we have computer systems running everywhere and in different \textit{contexts of use}, which involves three factors: the \textit{platform}, \textit{environment} and \textit{the user}~\cite{ui-eric-plasticity-vs-responsive}.
+Nowadays, with the rise of mobile devices such as notebooks, smartphones, smartwatches and tablets, there is computer systems running everywhere and in different \textit{contexts of use}, which involves three factors: the \textit{platform}, \textit{environment} and \textit{the user}~\cite{ui-eric-plasticity-vs-responsive}.
 These factors affect the interaction between the user and the system.
-This interaction happens through the \textit{user interface} (UI) and users have to deal with different UIs adapted to several contexts.
+This interaction happens through the \textit{user interface} (UI), and users have to deal with different UIs adapted to several contexts.
 Hence the term \textit{adaptable user interfaces}.
-All this allows us to see that today developing UIs can be as complex as developing the core of the system.
+All this allows to see that today developing UIs can be as complex as developing the core of the system.
 There are several questions to be considered, among them: quality.
@@
 It can be defined as a process, or a series of processes, designed to ensure computer code does what it was designed to do and, conversely, that it does not anything unintended~\cite{test-art-of-testing}.
-What is the impact of adaptable user interfaces in software testing?
-Are there tools ready to test these adaptable UIs?
+What is the impact of adaptable user interfaces on software testing?
+Are there already tools to test these adaptable UIs?
 
@@
 These UIs can be adapted to different devices or have different versions for the same device.
-For instance, we used as case study, a smart home energy management system prototype with four equivalent versions: three for web and one for mobile environment.
-This exposes the problem in which we focus: the repetitive work of writing test scripts for different versions of the UIs of the same system.
+For instance, we used as case study a smart home energy management system prototype with four equivalent versions: three for web and one for mobile environment.
+This exposes the problem which we focus: the repetitive work of writing and maintain test scripts for different versions of the UIs of the same system.
 

### 2015-07-07 paper.tex
Add genetic algorithm for testing's reference

--- 2015-07-07 paper.tex
@@
 - creating an abstraction of the UI which is then tested in place of the UI itself [TODO: ref Sophie's paper]
-- automated planning for hierarchical test case generation may be used which involves genetic algorithms [TODO: ref]
+- automated planning for hierarchical test case generation may be used which involves genetic algorithms [Ref: get https://en.wikipedia.org/wiki/Graphical_user_interface_testing#cite_note-Mem01-5]
 - using "capture and replay" method is rejected, as it would involve one capture per version [TODO: ref]

### 2015-07-07 paper.tex
Add Discussion to Approach

@@
 % =============================================================================
-Quality is very important in the software industry, and so are tests. They have been extensively studied by literature [TODO: some refs].
-In a more modern context, Continuous Integration (CI) has been gaining popularity, hence is the need of automated tests.
-An automated test is usually generated for the exact goal to achieve, then is executed and its results are compared to those expected, finally a report is constructed with a summary of the failures encountered.
-The report can be easily generated by IDE plugins as long as tests are well designed and use testing libraries (like JUnit).
-The increasing popularity of web-based softwares has obliged to develop tools to perform tests on these devices.
-Among them, are Selenium for browser-based applications, and Selendroid for Android applications.
-Furthermore, GUIs have proven to be difficult to test, requiring new ways to verify them.
-So automation of UI testing may be achieved by several means :
-- using Finite State Machine-based modeling which suffers scaling problems [TODO: ref]
-- creating an abstraction of the UI which is then tested in place of the UI itself [TODO: ref Sophie's paper]
-- automated planning for hierarchical test case generation may be used which involves genetic algorithms [Ref: get https://en.wikipedia.org/wiki/Graphical_user_interface_testing#cite_note-Mem01-5]
-- using "capture and replay" method is rejected, as it would involve one capture per version [TODO: ref]
+TODO
 
@@
 \subsection{Discussion and Analysis}
-TODO
+Firstly, the number of lines to write for tests have been at least halved, as Table \ref{table:scriptssize} shows it.
+\begin{table}
+\begin{tabular}{l l r r r r}
+			&					&	mobile	&	web0	&	web1	&	web2	\\
+goal		&	plain Java	&	161		&	143		&	151		&	147		\\
+			&	with Tobias	&	76		&	67		&	69		&	68		\\
+filter		&	plain Java	&	/		&	350		&	402		&	369		\\
+			&	with Tobias	&	/		&	88		&	93		&	92		\\
+compare	&	plain Java	&	/		&	/		&	235		&	227		\\
+			&	with Tobias	&	/		&	/		&	59		&	58
+\end{tabular}
+\caption{Comparison of number of lines for various functionalities and various versions for Tobias script and its generated test}
+\label{table:scriptssize}
+\end{table}
+Secondly, the logical structure of the various tests for a same functionality and version is shared, and so the differences between these files are very localized : in the header of the file (preferences for the test) and in the implementations of the abstract groups (version details).
+So there is little variation from a shared abstract script for each file, as can be seen in Table \ref{table:scripts-similarity}.
+\begin{table}
+\begin{tabular}{l l r r r}
+			&			&	shared	&	total	&	\%	\\
+goal		&	mobile	&	48		&	76		&	63	\\
+			&	web0	&	65		&	67		&	97	\\
+			&	web2	&	65		&	68		&	95	\\
+filter		&	web0	&	78		&	88		&	88	\\
+			&	web2	&	89		&	92		&	96	\\
+compare	&	web2	&	55		&	58		&	94
+\end{tabular}
+\caption{Comparison of number of shared lines between Tobias scripts and version web1 for a same functionality}
+\label{table:scripts-similarity}
+\end{table}
+When small changes are applied to the UI, the scripts only differ by some lines. Even in the case of a change of platform (web to mobile) the scripts stay similar.
+Lastly, there is also shared lines between files, whichever their version and functionality tested, because these tests proceed by steps, which can sometimes be the same for several scripts.
+So this approach allows to reduce the amount of work, while it facilitates it by reducing differences between script versions.
 

### 2015-07-07 paper.tex
Add a beginning to the conclusion

--- 2015-07-07 paper.tex
@@
 % =============================================================================
+Because of the similarities, these scripts could easily be generated from a single script, containing the abstract test cases and the implementation details.
+Tobias could do it if its entry language syntax (TSLT) would be improved.
 TODO

### 2015-07-07 paper.tex
Grammar correction

@@
 % =============================================================================
-TODO
+Nowadays, with the rise of mobile devices such as notebooks, smartphones, smartwatches and tablets, there is computer systems running everywhere and in different \textit{contexts of use}, which involves three factors: the \textit{platform}, \textit{environment} and \textit{the user}~\cite{ui-eric-plasticity-vs-responsive}.
+These factors affect the interaction between the user and the system.
+This interaction happens through the \textit{user interface} (UI), and users have to deal with different UIs adapted to several contexts.
+Hence the term \textit{adaptable user interfaces}.
+All this allows to see that today developing UIs can be as complex as developing the core of the system.
+There are several questions to be considered, among them: quality.
+\textit{Software Testing} is one of the most used ways in the industry to assure quality~\cite{test-hdr-lydie}.
+It can be defined as a process, or a series of processes, designed to ensure computer code does what it was designed to do and, conversely, that it does not anything unintended~\cite{test-art-of-testing}.
+What is the impact of adaptable user interfaces on software testing?
+Are there already tools to test these adaptable UIs?
+
+Answering these questions motivates the development of this project.
+In this work, we focus on the scenario of having different UIs for the same system.
+These UIs can be adapted to different devices or have different versions for the same device.
+For instance, we used as case study a smart home energy management system prototype with four equivalent versions: three for web and one for mobile environment.
+This exposes the problem which we focus: the repetitive work of writing and maintaining test scripts for different versions of the UIs of the same system.
+
+Our contribution is the approach of automatically generate test scripts for each version of the UI of the same system from scripts written in a higher-level language.
+In other words, testers would be able to write test cases for all the versions using abstract descriptions.
+A tool would be responsible for interpreting these descriptions and generating test scripts ready to be executed for each version of the UI.
+
+This paper is structured as follows.
+First, the related work is presented, explaining several concepts about test automation, UI testing and tools.
+Then, we explain the case study used in this research.
+Next, we show how test scripts can be generated from abstract descriptions using an existing tool.
+Finally, the conclusions that summarize our current results and proposed perspectives.
 
@@
 % =============================================================================
-Because of the similarities, these scripts could easily be generated from a single script, containing the abstract test cases and the implementation details.
-Tobias could do it if its entry language syntax (TSLT) would be improved.
 TODO

### 2015-07-07 paper.tex
Inicial proposal for the related work section

--- 2015-07-07 paper.tex
@@
 % =============================================================================
-TODO
+With the popularity of Continuous Integration (CI), a software engineering practice in which isolated changes are immediately tested and reported on when they are added to a larger code base, the need of test automation increased.
+Test automation can be analyzed in three ways: the generation of test scripts, the execution of tests and the analysis of the test results.
+The scientific community has developed several approaches and tools for automation of regular and UI testing.
+Some of them will be presented below.
+
+An example of automation for the generation of test script is Tobias~\cite{tobias}, a combinatorial tool that instantiates a large set of test sequences from an abstract description.
+Combinatorial testing allows to express a large set of test cases in a few lines.
+Tobias receives the abstractly written tests and generates an executable test code containing several possible combinations of execution, according to the specification of the abstract entry code.
+
+In the case of execution automation, several tools have been developed focusing on UI testing.
+They are tools that drive the UI as users do, triggering actions, navigating the system and checking the UI content.
+For instance, tools for web~\cite{watir, cucumber} and mobile~\cite{appium, selendroid} environments are responsible for interacting with the UI according to the scripts written by the testers.
+Besides, there are tools~\cite{selenium, monkeytalk} that are also able to generate test scripts, through the process of record and playback.
+The user interacts with the system, the tool records the actions generating a testing script that can be user for execution automation.
+
+Other interesting approach, proposed in~\cite{test-image-comparison-korea}, uses the idea of record and playblack with the automation of the analysis of the results through image comparison.
+In this solution, after the execution of a test script, the image of the UI is recorded.
+It can be used later to verify if changes in the system affected the UI, comparing automatically the old and new images of the UI.
+
+Another related work, presented in~\cite{ui-equilavance-raquel}, is not about testing, but comparing UIs of the same system that are adapted to different contexts.
+In this approach, the UIs are abstracted to formal models based on graphs and the abstracts can be automatically compared, verifying if  they have the same capabilities and appearance.
 

### 2015-07-08 paper.tex
Correcting some mistakes in Nelson's Related Work

--- 2015-07-07 paper.tex
@@
 % =============================================================================
-TODO
+With the popularity of Continuous Integration (CI), a software engineering practice in which isolated changes are immediately tested and reported on when they are added to a larger code base, the need of test automation has increased.
+Test automation can be achieved by three ways: the generation of test scripts, their execution and the analysis of the results.
+The scientific community has developed several approaches and tools for automation of regular and UI testing.
+Some of them will be presented below.
+
+An example of automation for the generation of test scripts is Tobias~\cite{tobias}, a combinatorial tool that instantiates a large set of test sequences from an abstract description.
+Combinatorial testing allows to express a large set of test cases in a few lines.
+Tobias receives the abstract test and generates an executable test code containing several possible combinations of execution, according to the specification of the abstract code given.
+
+In the case of execution automation, several tools have been developed focusing on UI testing.
+There are tools that drive the UI as users do, triggering actions, navigating the system and checking the UI content.
+For instance, tools for web~\cite{watir, cucumber} and mobile~\cite{appium, selendroid} environments are responsible for interacting with the UI according to the scripts written by the testers.
+Besides, there are tools~\cite{selenium, monkeytalk} that are also able to generate test scripts, through the process of record and playback.
+The user interacts with the system, the tool records the actions, thus generating a test script that can be used thereafter for execution automation.
+
+Another interesting approach, proposed in~\cite{test-image-comparison-korea}, uses the idea of record and playblack with the automation of the analysis of the results through image comparison.
+In this solution, after the execution of a test script, the image of the UI is recorded.
+It can be used later to verify if changes in the system affected the UI, comparing automatically the old and new images of the UI.
+
+Another related work, presented in~\cite{ui-equilavance-raquel}, is not strictly about testing, but comparing UIs of the same system that are adapted to different contexts.
+In this approach, the UIs are abstracted to formal models based on graphs and the abstractions can be automatically compared, verifying if  they have the same capabilities and appearance.
 

### 2015-07-08 paper.tex
First part of the case study section

--- 2015-07-07 paper.tex
@@
 % =============================================================================
-With the popularity of Continuous Integration (CI), a software engineering practice in which isolated changes are immediately tested and reported on when they are added to a larger code base, the need of test automation increased.
-Test automation can be analyzed in three ways: the generation of test scripts, the execution of tests and the analysis of the test results.
-The scientific community has developed several approaches and tools for automation of regular and UI testing.
-Some of them will be presented below.
-
-An example of automation for the generation of test script is Tobias~\cite{tobias}, a combinatorial tool that instantiates a large set of test sequences from an abstract description.
-Combinatorial testing allows to express a large set of test cases in a few lines.
-Tobias receives the abstractly written tests and generates an executable test code containing several possible combinations of execution, according to the specification of the abstract entry code.
-
-In the case of execution automation, several tools have been developed focusing on UI testing.
-They are tools that drive the UI as users do, triggering actions, navigating the system and checking the UI content.
-For instance, tools for web~\cite{watir, cucumber} and mobile~\cite{appium, selendroid} environments are responsible for interacting with the UI according to the scripts written by the testers.
-Besides, there are tools~\cite{selenium, monkeytalk} that are also able to generate test scripts, through the process of record and playback.
-The user interacts with the system, the tool records the actions generating a testing script that can be user for execution automation.
-
-Other interesting approach, proposed in~\cite{test-image-comparison-korea}, uses the idea of record and playblack with the automation of the analysis of the results through image comparison.
-In this solution, after the execution of a test script, the image of the UI is recorded.
-It can be used later to verify if changes in the system affected the UI, comparing automatically the old and new images of the UI.
-
-Another related work, presented in~\cite{ui-equilavance-raquel}, is not about testing, but comparing UIs of the same system that are adapted to different contexts.
-In this approach, the UIs are abstracted to formal models based on graphs and the abstracts can be automatically compared, verifying if  they have the same capabilities and appearance.
+TODO
 
@@
 \section{Case Study}
-% =============================================================================
-TODO
+The case study used in this work is a prototype for a smart home energy management system.
+This decision is based on the fact that it is a modern concept, little explored in the domain of this research and whose UIs can be adapted to several contexts.
+A smart home may be defined as a well-designed structure with sufficient access to assets, communication, controls, data, and information technologies for enhancing the occupants' quality of life through comfort, convenience, reduced costs and increased connectivity~\cite{smart-home-harper}.
+A smart home energy management system is an energy management system applied to smart homes.
+It allows users to control and monitor the energy consumption in a residence from different devices.
+
+It is a prototype because we have developed only the UIs of the system for four versions, three for web environment and one as a mobile application.
+The data of the system are predetermined.
+All versions have the same features, except for two web versions that have an additional feature.
+The differences between the versions are visual.
+In the case of the mobile application, the UI is adapted to a mobile device, which contains a smaller screen and its own platform for UI development.
+In the case of the web versions, the UIs have also been developed to this context, using web UI technologies.
+But the differences between the three web versions are changes in the navigation and UI components.
+In this paper, we focus on the following features of the prototype:
+
+\begin{enumerate}
+
+\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month.
+
+\item \textbf{Filter}: the user has access to a list of all his or her objects in the house, having the possibility to filter this list per room.
+An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices.
+
+\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions.
+
+\end{enumerate}
 

### 2015-07-08 paper.tex
Testing Web and Mobile screenshots in the paper

--- 2015-07-08 paper.tex
@@
 % =============================================================================
-Nowadays, with the rise of mobile devices such as notebooks, smartphones, smartwatches and tablets, there is computer systems running everywhere and in different \textit{contexts of use}, which involves three factors: the \textit{platform}, \textit{environment} and \textit{the user}~\cite{ui-eric-plasticity-vs-responsive}.
-These factors affect the interaction between the user and the system.
-This interaction happens through the \textit{user interface} (UI), and users have to deal with different UIs adapted to several contexts.
-Hence the term \textit{adaptable user interfaces}.
-All this allows to see that today developing UIs can be as complex as developing the core of the system.
-There are several questions to be considered, among them: quality.
-\textit{Software Testing} is one of the most used ways in the industry to assure quality~\cite{test-hdr-lydie}.
-It can be defined as a process, or a series of processes, designed to ensure computer code does what it was designed to do and, conversely, that it does not anything unintended~\cite{test-art-of-testing}.
-What is the impact of adaptable user interfaces on software testing?
-Are there already tools to test these adaptable UIs?
-
-Answering these questions motivates the development of this project.
-In this work, we focus on the scenario of having different UIs for the same system.
-These UIs can be adapted to different devices or have different versions for the same device.
-For instance, we used as case study a smart home energy management system prototype with four equivalent versions: three for web and one for mobile environment.
-This exposes the problem which we focus: the repetitive work of writing and maintaining test scripts for different versions of the UIs of the same system.
-
-Our contribution is the approach of automatically generate test scripts for each version of the UI of the same system from scripts written in a higher-level language.
-In other words, testers would be able to write test cases for all the versions using abstract descriptions.
-A tool would be responsible for interpreting these descriptions and generating test scripts ready to be executed for each version of the UI.
-
-This paper is structured as follows.
-First, the related work is presented, explaining several concepts about test automation, UI testing and tools.
-Then, we explain the case study used in this research.
-Next, we show how test scripts can be generated from abstract descriptions using an existing tool.
-Finally, the conclusions that summarize our current results and proposed perspectives.
+TODO
 
@@
 % =============================================================================
-With the popularity of Continuous Integration (CI), a software engineering practice in which isolated changes are immediately tested and reported on when they are added to a larger code base, the need of test automation has increased.
-Test automation can be achieved by three ways: the generation of test scripts, their execution and the analysis of the results.
-The scientific community has developed several approaches and tools for automation of regular and UI testing.
-Some of them will be presented below.
-
-An example of automation for the generation of test scripts is Tobias~\cite{tobias}, a combinatorial tool that instantiates a large set of test sequences from an abstract description.
-Combinatorial testing allows to express a large set of test cases in a few lines.
-Tobias receives the abstract test and generates an executable test code containing several possible combinations of execution, according to the specification of the abstract code given.
-
-In the case of execution automation, several tools have been developed focusing on UI testing.
-There are tools that drive the UI as users do, triggering actions, navigating the system and checking the UI content.
-For instance, tools for web~\cite{watir, cucumber} and mobile~\cite{appium, selendroid} environments are responsible for interacting with the UI according to the scripts written by the testers.
-Besides, there are tools~\cite{selenium, monkeytalk} that are also able to generate test scripts, through the process of record and playback.
-The user interacts with the system, the tool records the actions, thus generating a test script that can be used thereafter for execution automation.
-
-Another interesting approach, proposed in~\cite{test-image-comparison-korea}, uses the idea of record and playblack with the automation of the analysis of the results through image comparison.
-In this solution, after the execution of a test script, the image of the UI is recorded.
-It can be used later to verify if changes in the system affected the UI, comparing automatically the old and new images of the UI.
-
-Another related work, presented in~\cite{ui-equilavance-raquel}, is not strictly about testing, but comparing UIs of the same system that are adapted to different contexts.
-In this approach, the UIs are abstracted to formal models based on graphs and the abstractions can be automatically compared, verifying if  they have the same capabilities and appearance.
+TODO
 
@@
 \section{Case Study}
+% =============================================================================
+
+\marginpar{
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
+  \caption{Une figure dans la marge.}
+  \label{fig:marginparsample}
+  \end{center}  
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
+  \caption{Une figure dans la marge.}
+  \label{fig:marginparsample}
+  \end{center}  
+\end{figure}
+}
+
 The case study used in this work is a prototype for a smart home energy management system.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{images/web0_goal-filter.eps}
+  \caption{Ajoutez une légende en dessous de chaque image.}
+  \label{fig:sample}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{images/mobile_goal-filter.eps}
+  \caption{Ajoutez une légende en dessous de chaque image.}
+  \label{fig:sample}
+\end{figure}
+
 % =============================================================================

### 2015-07-08 paper.tex

--- 2015-07-08 paper.tex
@@
 \end{enumerate}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{images/web0_goal-filter.eps}
+  \caption{Ajoutez une légende en dessous de chaque image.}
+  \label{fig:sample}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{images/mobile_goal-filter.eps}
+  \caption{Ajoutez une légende en dessous de chaque image.}
+  \label{fig:sample}
+\end{figure}
 

### 2015-07-08 paper.tex
Adding comparator feature screenshot for the case study
First version of the case study with the images

@@
 
+\marginpar{
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
+  \caption{Web version. Number 1 represents the \textbf{goal} feature and number 2 represents the \textbf{filter} feature.}
+  \label{fig:web0print}
+  \end{center}  
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
+  \caption{Mobile version. Number 1 represents the \textbf{goal} feature and number 2 represents the \textbf{filter} feature.}
+  \label{fig:mobileprint}
+  \end{center}  
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=\marginparwidth]{images/web1_comparator.eps}
+  \caption{Other web version. Number 3 represents the \textbf{comparator} feature.}
+  \label{fig:web1print}
+  \end{center}  
+\end{figure}
+}
+
 Another interesting approach, proposed in~\cite{test-image-comparison-korea}, uses the idea of record and playblack with the automation of the analysis of the results through image comparison.
@@
 % =============================================================================
-
-\marginpar{
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
-  \caption{Une figure dans la marge.}
-  \label{fig:marginparsample}
-  \end{center}  
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
-  \caption{Une figure dans la marge.}
-  \label{fig:marginparsample}
-  \end{center}  
-\end{figure}
-}
 
@@
 \begin{enumerate}
-
-\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month.
+\item \textbf{Goal}: the user can check information about the general energy consumption per month.
+Having access to the goal and consumption in kWh for the chosen month.
+See \autoref{fig:web0print} and \autoref{fig:mobileprint}.
 
@@
 An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices.
+See \autoref{fig:web0print} and \autoref{fig:mobileprint}.
 
-\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions.
-
+\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts.
+This feature is present in only two of the web versions.
+See \autoref{fig:web1print}
 \end{enumerate}
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{images/web0_goal-filter.eps}
-  \caption{Ajoutez une légende en dessous de chaque image.}
-  \label{fig:sample}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{images/mobile_goal-filter.eps}
-  \caption{Ajoutez une légende en dessous de chaque image.}
-  \label{fig:sample}
-\end{figure}
+The purpose is to test each feature using execution automation tools for UI testing.
+For instance Selenium~\cite{selenium} for the web versions and Selendroid~\cite{selendroid} for the mobile version.
+The approach to test the \textbf{goal} feature is to make these tools to change the current month, interacting with the combobox filter component, and then to verify if the goal and consumed labels have the right value.
+In the case of the \textbf{filter} feature, the tools have to interact with the filter, changing the current room and verifying if the only correct objects are displayed in the screen.
+Finally, the \textbf{compator} feature can be tested by using the tools to change the room filter, to chose the objects using the checkbox and to verify if the charts are displayed.
 

### 2015-07-09 paper.tex
Adding support for Windows-compiling when eps images included
Adding borders to results tables in Approch section

--- 2015-07-08 paper.tex
@@
 % =============================================================================
-
-\marginpar{
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
-  \caption{Une figure dans la marge.}
-  \label{fig:marginparsample}
-  \end{center}  
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
-  \caption{Une figure dans la marge.}
-  \label{fig:marginparsample}
-  \end{center}  
-\end{figure}
-}
-
-The case study used in this work is a prototype for a smart home energy management system.
-This decision is based on the fact that it is a modern concept, little explored in the domain of this research and whose UIs can be adapted to several contexts.
-A smart home may be defined as a well-designed structure with sufficient access to assets, communication, controls, data, and information technologies for enhancing the occupants' quality of life through comfort, convenience, reduced costs and increased connectivity~\cite{smart-home-harper}.
-A smart home energy management system is an energy management system applied to smart homes.
-It allows users to control and monitor the energy consumption in a residence from different devices.
-
-It is a prototype because we have developed only the UIs of the system for four versions, three for web environment and one as a mobile application.
-The data of the system are predetermined.
-All versions have the same features, except for two web versions that have an additional feature.
-The differences between the versions are visual.
-In the case of the mobile application, the UI is adapted to a mobile device, which contains a smaller screen and its own platform for UI development.
-In the case of the web versions, the UIs have also been developed to this context, using web UI technologies.
-But the differences between the three web versions are changes in the navigation and UI components.
-In this paper, we focus on the following features of the prototype:
-
-\begin{enumerate}
-
-\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month.
-
-\item \textbf{Filter}: the user has access to a list of all his or her objects in the house, having the possibility to filter this list per room.
-An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices.
-
-\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions.
-
-\end{enumerate}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{images/web0_goal-filter.eps}
-  \caption{Ajoutez une légende en dessous de chaque image.}
-  \label{fig:sample}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{images/mobile_goal-filter.eps}
-  \caption{Ajoutez une légende en dessous de chaque image.}
-  \label{fig:sample}
-\end{figure}
+TODO
 
@@
 \subsection{Discussion and Analysis}
-TODO
+Firstly, the number of lines to write for tests have been at least halved, as Table \ref{table:scriptssize} shows it.
+\begin{table}
+\begin{tabular}{|l l|r r r r|}
+\hline
+test		&	implementation&	mobile	&	web0	&	web1	&	web2	\\
+\hline
+goal		&	plain Java	&	161		&	143		&	151		&	147		\\
+			&	with Tobias	&	76		&	67		&	69		&	68		\\
+\hline
+filter		&	plain Java	&	/		&	350		&	402		&	369		\\
+			&	with Tobias	&	/		&	88		&	93		&	92		\\
+\hline
+compare	&	plain Java	&	/		&	/		&	235		&	227		\\
+			&	with Tobias	&	/		&	/		&	59		&	58		\\
+\hline
+\end{tabular}
+\caption{Comparison of number of lines for various functionalities and various versions for Tobias script and its generated test}
+\label{table:scriptssize}
+\end{table}
+Secondly, the logical structure of the various tests for a same functionality and version is shared, and so the differences between these files are very localized : in the header of the file (preferences for the test) and in the implementations of the abstract groups (version details).
+So there is little variation from a shared abstract script for each file, as can be seen in Table \ref{table:scripts-similarity}.
+\begin{table}
+\begin{tabular}{|l l|r r r|}
+\hline
+test		&	version&	shared	&	total	&	\%	\\
+\hline
+goal		&	mobile	&	48		&	76		&	63	\\
+			&	web0	&	65		&	67		&	97	\\
+			&	web2	&	65		&	68		&	95	\\
+\hline
+filter		&	web0	&	78		&	88		&	88	\\
+			&	web2	&	89		&	92		&	96	\\
+\hline
+compare	&	web2	&	55		&	58		&	94 \\
+\hline
+\end{tabular}
+\caption{Comparison of number of shared lines between Tobias scripts and version web1 for a same functionality}
+\label{table:scripts-similarity}
+\end{table}
+When small changes are applied to the UI, the scripts only differ by some lines. Even in the case of a change of platform (web to mobile) the scripts stay similar.
+Lastly, there is also shared lines between files, whichever their version and functionality tested, because these tests proceed by steps, which can sometimes be the same for several scripts.
+So this approach allows to reduce the amount of work, while it facilitates it by reducing differences between script versions.
 
